Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-29 paper.tex
add abstract and finish intro

\begin{abstract}
TODO: Write this abstract.
\end{abstract}

@@

TODO: add good intro/overview paragraph

@@

Due to the diversity of fuel cycle simulators' modeling assumptions direct
comparison and benchmarking can be difficult.  In 2012 the Organisation for
Economic Co-operation and Development (OECD) completed a benchmark study
\cite{oecd2012benchmark} that is perhaps one of the most complete published
comparisons performed.  Despite this, however, various results from the
different simulators were often significantly different due to different
modeling decisions such as reprocessing strategies, refueling behavior,
reactor end-of-life handling, etc.

>>>>

\begin{abstract}

Due to the diversity of fuel cycle simulators' modeling assumptions direct
comparison and benchmarking can be difficult.  In 2012 the Organisation for
Economic Co-operation and Development (OECD) completed a benchmark study that
is perhaps one of the most complete published comparisons performed.  Despite
this, however, various results from the simulators were often significantly
different due to inconsistency in modeling decisions such as reprocessing
strategies, refueling behavior, reactor end-of-life handling, etc.  This work
attempts to identify and quantify the effects of a few different modeling
choices that may sometimes be taken for granted in the fuel cycle modeling
domain.  Four scenarios were compared using combinations of fleet-based or
individual reactors with monthly or quarterly (3-month) time steps.  When
under supply-constraint pressure, the four cases exhibit noticably different
behavior.  Otherwise, they generally behaved very similarly.  Fleet-based
modeling is more efficient in supply-constrained environments at the expense
of losing insight on issues such as reactor refueling cycle staggering.
Finer-grained time steps also enable more efficient material use in
supply-constrained environments. Large simulations with fleet-based reactors
run much more quickly than their individual reactor counterparts.

\end{abstract}

@@

Due to the diversity of fuel cycle simulators' modeling assumptions direct
comparison and benchmarking can be difficult.  In 2012 the Organisation for
Economic Co-operation and Development (OECD) completed a benchmark study
\cite{oecd2012benchmark} that is perhaps one of the most complete published
comparisons performed.  Despite this, however, various results from the
different simulators were often significantly different due to different
modeling decisions such as reprocessing strategies, refueling behavior,
reactor end-of-life handling, etc.  This work attempts to identify and
quantify the effects of a few different modeling choices that may sometimes be
taken for granted in the fuel cycle modeling domain: facility modeling
discretization (i.e. individual facilities vs. aggregate fleets) and time step
duration.  A better understanding of how these affect fuel cycle dynamics can
allow for making more deliberate decisions with respect to tradeoffs such as
performance vs. realism.

@@
